---
title: "Presentation Title"
subtitle: "Subtitle or event name"
author: "Author Name"
date: last-modified
date-format: "D MMMM YYYY"
format:
  uog-slides-revealjs:
    footer: "University of Glasgow"
    chalkboard: true # enable writing on top of slides
---

# Introduction {.section-slide}

## Slide with bullets

- First point about the topic
- Second point with **bold** emphasis
- Third point with `inline code`

## Slide with two columns

:::: {.columns}
::: {.column width="50%"}
**Left column**

Some content here — text, a list, or a figure.
:::
::: {.column width="50%"}
**Right column**

More content on the right side of the slide.
:::
::::

## Slide with a figure

```{r}
#| echo: false
#| fig-height: 4
plot(cars, col = "#011451", pch = 19,
     xlab = "Speed", ylab = "Distance")
```

## Slide with a table

| Column A | Column B | Column C |
|----------|----------|----------|
| Value 1  | 12.3     | Yes      |
| Value 2  | 45.6     | No       |
| Value 3  | 78.9     | Yes      |

# Methods {.section-slide}

## Code example

```{r}
#| eval: false
#| echo: true
library(ggplot2)

ggplot(cars, aes(x = speed, y = dist)) +
  geom_point(colour = "#011451") +
  labs(x = "Speed", y = "Distance")
```

## Callout boxes

::: {.callout-note}
This is a note — extra context or references.
:::

::: {.callout-tip}
This is a tip — a helpful suggestion.
:::

::: {.callout-important}
This is important — don't miss it.
:::

# Results {.section-slide}

## Key finding

Something interesting happened here.

- Bullet one
- Bullet two

> A blockquote for emphasis or a key quote.

# Summary {.section-slide}

## Take-aways

1. First take-away
2. Second take-away
3. Third take-away

## Thank you {.center}

::: {style="margin-left: 12%;"}
Questions?
:::

::: {style="font-size: 0.7em; margin-top: 1em; margin-left: 12%;"}
[your.email@glasgow.ac.uk](mailto:your.email@glasgow.ac.uk)
:::
